%! TeX program = lualatex
\documentclass[../main.tex]{subfiles}
\begin{document} 

The chain rule.
\begin{enumerate}
  \item Decompose \(e^{2x + 1}\) as \(f(u)\) so that \(e^{2x + 1} = f(u)\).  

  \item Differentiate \(e^{2x+1}\).
\end{enumerate}

The chain rule with exponential-like functions.
\begin{enumerate}
  \item Decompose \(x^{x}\) as \(f(u)\) so that \(f(u) = x^{x}\).

  \item Differentiate \(x^{x}\).
\end{enumerate}

The chain rule with exponential-like functions.
\begin{enumerate}
  \item Decompose \((x^{2}+1)^{\sin(x)}\).  
  \item Differentiate \((x^{2}+1)^{\sin(x)}\).
\end{enumerate}

Derivatives of inverse functions.
\begin{enumerate}
  \item Simplify the expression \(\sec(y)\) where \(x = \tan(y)\), or equivalently, simplify the expression \(\sec(\arctan(x))\).
  \item Find the derivative of \(\arctan(x)\).
\end{enumerate}

Derivatives of inverse functions.
\begin{enumerate}
  \item Simplify \(\frac{1}{\cos(\arcsin(x))}\).
  \item Find the derivative of \(\arcsin(x^{3})\).
\end{enumerate}

Related rates and implicit differentiation.
\begin{enumerate}
  \item Implicitly differentiate \(\tan(\theta) = \frac{x}{3}\) with respect to \(t\).
  \item Related rates: the fish example.
\end{enumerate}

Related rates and implicit differentiation.
\begin{enumerate}
  \item Find \(\frac{dy}{dt}\) given that \(x^{2} + 4000^{2} = y^{2}\) and \(\frac{dx}{dt} = 600\) at \(x = 3000\).

  \item The plane example.
\end{enumerate}

Related rates and implicit differentiation.
\begin{enumerate}
  \item Find \(\frac{dh}{dt}\) given that \(V = \frac{h^{3}}{12}\) and \(\frac{dV}{dt} = 2\) at \(h = 2\).

  \item Inverted pyramid example.
\end{enumerate}

Critical numbers and optimization.
\begin{enumerate}
  \item Minimize \(s\) given \(T(s) = \frac{2 - 6\sqrt{s^{2} - 1}}{6} + \frac{s}{3}\) on the domain \(1 \le s \le \sqrt{5}\).
  \item River crossing example.
\end{enumerate}

Working with equations and antiderivative.
\begin{enumerate}
  \item Given \(F(x) = - \cos(x) - \ln|x| + 2x + C\) and \(F(1) = 3\), find \(C\).

  \item Suppose \(F(x)\) given that \(F'(x) = \sin(x) - \frac{1}{x} + \sec^{2}(\pi/4)\) and \(F(1) = 3\). 
\end{enumerate}

Limit of sums and integration.
\begin{enumerate}
  \item Evaluate \(\lim_{n \to \infty} \sum_{i=1}^{n} \frac{1}{n} \left( \frac{1}{n} \right)^{2}\).
  \item Use the definition to find the area under the curve \(y = x^{2}\) on \([0,1]\).
\end{enumerate}

FTC part 1.
\begin{enumerate}
  \item Differentiate \(\int_{0}^{x} e^{t^{2}} \;dt\).
  \item Differentiate \(\int_{0}^{x^{2}+1} e^{t^{2}} \;dt\).
  \item Differentiate \(\int_{x^{3}}^{x^{2}+1} e^{t^{2}} \;dt\).
\end{enumerate}
\end{document}
